---
title: "Chart examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Chart examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(chartjs4r)
library(ggplot2) # cross comparisons
```

## Introduction

A vignette to explore the functions of `chartjs4r`!

## bar chart

```{r}
# example data shipped with the package
cjs_example_data('bar')
```

A simple call. We often need to build further from here.

```{r, out.width='100%'}
cjs_example_data('bar') %>%
  chartjs(type = 'bar', x = letters, y = numbers)
```

Adding axis and themes.

```{r, out.width='100%'}
cjs_example_data('bar') %>%
  chartjs(type = 'bar', x = letters, y = numbers) %>% 
  cjs_scale_cartesian(id = 'y', title.text = 'count',
                      ticks = cjs_ticks(callback = ticks_integer_callback(step = 1))) %>% 
  cjs_scale_category(id = 'x', labels = month.name[1:5],
                     grid = cjs_grid(display = FALSE)) %>% 
  cjs_theme(title.text = 'A Chart.js plot', legend.position = 'none')
```

Adding datasets.

```{r, out.width='100%'}
cjs_example_data('bar') %>%
  chartjs() %>% 
  cjs_add_bars(x = letters, y = numbers, label = 'from source data') %>% 
  cjs_add_bars(x = LETTERS[1:5], y = 5:1, label = 'from vectors') %>% 
  cjs_add_bars(x = x1, y = y1, label = 'from given data',
               data = data.frame(x1 = LETTERS[1:5], y1 = rpois(5,5))) %>% 
  cjs_scale_color(backgroundColors = c('#181E20', '#045C94','#FFBB1C'))
```

Stacking dataset sets - stacked bar plot

```{r, out.width='100%'}
cjs_example_data('bar') %>%
  chartjs() %>% 
  cjs_add_bars(x = letters, y = numbers, label = 'from source data') %>% 
  cjs_add_bars(x = LETTERS[1:5], y = 5:1, label = 'from vectors') %>% 
  cjs_add_bars(x = x1, y = y1, label = 'from given data',
               data = data.frame(x1 = LETTERS[1:5], y1 = rpois(5,5))) %>% 
  cjs_scale_color(backgroundColors = c('#181E20', '#045C94','#FFBB1C')) %>% 
  cjs_stack_bars()
```

Horizontal bar plot

```{r, out.width='100%'}
cjs_example_data('bar') %>%
  chartjs(type = 'bar') %>% 
  cjs_add_bars(x = letters, y = numbers, colors = palette()[1:5]) %>% 
  cjs_bar_orientation('horizontal')
```

TODO - time axis .. fix time data as ggplot2

```{r, out.width='100%'}
cjs_example_data('scatter') %>% 
  chartjs() %>% 
  cjs_add_bars(x = x_time, y = y_numbers)
```

```{r}
# expands data
cjs_example_data('scatter') %>% 
  ggplot() +
  geom_col(aes(x = x_time, y = y_numbers))
```


## scatter chart

```{r}
# example data shipped with the package
cjs_example_data('scatter')
```

Call with axes specs.

```{r, out.width='100%'}
cjs_example_data('scatter') %>%
  chartjs(type = 'scatter', x = x_numbers, y = y_numbers) %>% 
  # fix documentation of these
  cjs_scale_cartesian(id = 'y', title.text = 'Numbers on Y',
                      min = -0.2, max = 1.2) %>% 
  cjs_scale_cartesian(id = 'x', title.text = 'Numbers on X',
                      min = -0.2, max = 1.2)
```

Adding datasets and colouring

```{r, out.width='100%'}
cjs_example_data('scatter') %>%
  chartjs() %>% 
  cjs_add_points(x = x_numbers, y = y_numbers, label = 'from source data') %>% 
  cjs_add_points(x = runif(12), y = runif(12), label = 'from vectors') %>% 
  cjs_add_points(x = x1, y = y1, label = 'from given data',
                 data = data.frame(x1 = runif(12), y1 = runif(12))) %>% 
  cjs_scale_color(backgroundColors = palette()[1:3])
```

Adding a line to the points

```{r, out.width='100%'}
cjs_example_data('scatter') %>%
  chartjs() %>% 
  cjs_add_points(x = x_numbers, y = y_numbers, label = 'a', show_line = TRUE)
```

```{r}
# arranges data
cjs_example_data('scatter') %>% 
  ggplot(aes(x = x_numbers, y = y_numbers)) +
  geom_point() +
  geom_line()
```

Point shape and sizes

```{r, out.width='100%'}
unlist(cjs_shapes)

cjs_example_data('scatter') %>%
  chartjs() %>% 
  cjs_add_points(x = x_numbers, y = y_numbers, label = 'a') %>% 
  cjs_add_points(x = runif(12), y = runif(12), label = 'b') %>% 
  cjs_add_points(x = x1, y = y1, label = 'c', data = data.frame(x1 = runif(12), y1 = runif(12))) %>% 
  cjs_scale_color(backgroundColors = c(a = '#181E20', b = '#045C94', c = '#FFBB1C'), match_background_and_border = T) %>% 
  cjs_scale_shape(pointStyles = c(cjs_shapes$circle, 'cross', cjs_shapes[['star']])) %>% 
  cjs_scale_size(pointRadii = c(5,10,2))
```

## Doughnut and pie charts

Doughnut and pie fit in the same realm - `doughnut_pie` with a `type=` parameter

```{r}
cjs_example_data('doughnut_pie')
```

Doughnut

```{r}
cjs_example_data('doughnut_pie') %>% 
  chartjs() %>% 
  cjs_add_doughnut_pie(type = 'doughnut', x = letters, y = numbers)
```

Can stack .. needs work/QA

```{r}
cjs_example_data('doughnut_pie') %>% 
  chartjs() %>% 
  cjs_add_doughnut_pie(type = 'doughnut', x = letters, y = numbers) %>% 
  cjs_add_doughnut_pie(type = 'doughnut', x = LETTERS[1:5], y = 1:5)
```

Pie 

```{r}
cjs_example_data('doughnut_pie') %>% 
  chartjs() %>% 
  cjs_add_doughnut_pie(type = 'pie', x = letters, y = numbers, colors = palette()[1:5])
```

## cjs_theme

Needs work

```{r, out.width='100%'}
cjs_example_data('bar') %>%
  chartjs(type = 'bar', x = letters, y = numbers) %>% 
  cjs_theme(chart.backgroundColor = 'pink', 
            title.text = 'A pink chart',
            legend.position = 'right')
```
