---
title: "Date-time formatting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Date-time formatting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(chartjs4r)
library(ggplot2) # cross comparisons
```

## Introduction

Chartjs does not ship with a date formatter, and relies on extensions. This package
has included `chartjs-adapter-date-fns`(https://github.com/chartjs/chartjs-adapter-date-fns),
which comes from `https://date-fns.org/` . Finding the format page of latter's doc is
essential. Here are some examples.

The scatter example data, ships with a date column, with random values within the month of January 2023.

```{r}
cjs_example_data('scatter')
```

Since the function always returns random dates, we'll hard set them by creating an object

```{r}
time_data <- cjs_example_data('scatter')
```

The two thing to look out for with time scales in chartjs are the parameters - `time.unit` and `time.displayFormats`.

```{r, out.width='100%'}
time_data %>% 
  chartjs() %>% 
  cjs_add_bars(x = x_time, y = y_numbers) %>% 
  cjs_scale_datetime(id = 'x', time.unit = 'day')
```

We use `time.displayFormats` to format dates - search https://date-fns.org for 
date formats (at time of writing https://date-fns.org/v2.29.3/docs/format).

```{r, out.width='100%'}
time_data %>% 
  chartjs() %>% 
  cjs_add_bars(x = x_time, y = y_numbers) %>% 
  cjs_scale_datetime(id = 'x', time.unit = 'day', time.displayFormats = 'dd/MM/yyyy')
```

```{r, out.width='100%'}
time_data %>% 
  chartjs() %>% 
  cjs_add_bars(x = x_time, y = y_numbers) %>% 
  cjs_scale_datetime(id = 'x', time.unit = 'day', time.displayFormats = 'do LLL yyyy')
```

```{r, out.width='100%'}
time_data %>% 
  chartjs() %>% 
  cjs_add_bars(x = x_time, y = y_numbers) %>% 
  cjs_scale_datetime(id = 'x', time.unit = 'day', time.displayFormats = 'EEEE')
```

```{r}
time_data %>% 
  chartjs() %>% 
  cjs_add_bars(x = x_time, y = y_numbers) %>% 
  cjs_scale_datetime(id = 'x', time.unit = 'month', time.displayFormats = 'LLLL yyyy')
```

```{r}
# 12 rows exist, create a monthly data set
time_data2 <- time_data 
time_data2$x_time <- seq.Date(from = as.Date('2023-01-01'), to = as.Date('2023-12-01'), by = 'month')

time_data2 %>% 
  chartjs() %>% 
  cjs_add_bars(x = x_time, y = y_numbers) %>% 
  cjs_scale_datetime(id = 'x', time.unit = 'month', time.displayFormats = 'LLLL yyyy')
```

### Times

Default

```{r}
# 12 rows exist, create a hourly data
time_data2$x_time <- sample(size = 12, x = seq.POSIXt(from = as.POSIXct('2023-01-01 00:00:01'), to = as.POSIXct('2023-01-01 23:59:59'), by = 'hour'))

time_data2 %>% 
  chartjs() %>% 
  cjs_add_bars(x = x_time, y = y_numbers) %>% 
  cjs_scale_datetime(id = 'x', time.unit = 'hour')
```

```{r}
time_data2 %>% 
  chartjs() %>% 
  cjs_add_bars(x = x_time, y = y_numbers) %>% 
  cjs_scale_datetime(id = 'x', time.unit = 'hour', time.displayFormats = 'HHmm')
```

```{r}
time_data2 %>% 
  chartjs() %>% 
  cjs_add_bars(x = x_time, y = y_numbers) %>% 
  cjs_scale_datetime(id = 'x', time.unit = 'hour', time.displayFormats = 'h:mm a')
```
