---
title: "global-defaults"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{global-defaults}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

```{r setup}
#library(chartjs4r)
devtools::load_all()
```

## Introduction

We can set the defaults for all chartjs charts in a document using `cjs_defaults()`.
The list of chartjs defaults can be found in the javascript object `Chart.defaults`.

> This function alters the Chartjs.defaults inplace, and creating incorrect settings
can have undesired side-effects. So be careful!

For example, we can see the `borderColor` is a single value, while  `font` is a
list of options

```{js, eval=F}
// In browser console (javascript)
Chart.defaults
```

```{}
...
borderColor: "pink"
...
font: {
    "family": "'Helvetica Neue', 'Helvetica', 'Arial', sans-serif",
    "size": 16,
    "style": "normal",
    "lineHeight": 1.2
}
...
```

Thus we need to pass a similar object if we wish to change them. `cjs_defaults()` will 
cycle through the parameters provided and update the `Chart.defaults` object.

```{r}
# font is a list
cjs_defaults(borderColor = 'pink', font = list(size = 16))
```

Now all of the remaining plots will have pink `borderColor`

```{r, out.width='100%'}
chartjs() |>
  cjs_add_points(x = 1:10,
                 y = rnorm(10),
                 show_line = T)
```


```{r, out.width='100%'}
chartjs() |>
  cjs_add_bars(x = letters[1:3],
               y = rpois(3, 10))
```
