---
title: "Tooltips and interaction modes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tooltips and interaction modes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(chartjs4r)
```

## Tool tips

Default tool tips

```{r}
cjs_example_data('bar', grouped = TRUE) %>% 
  chartjs(type = 'bar', x = letters, y = numbers, group = group)
```

`cjs_tooltip` has various text positions above and below 'title', 'label' and 'footer.
They require single values for across all tooltips, or template literals to apply particular
values of the data to a tooltip.

```{r}
# Single values everywhere
chartjs() %>%
  cjs_add_bars(x = letters, y = numbers, label = 'Data 1', data = cjs_example_data('bar')) %>% 
  cjs_add_bars(x = letters, y = numbers, label = 'Data 2', data = cjs_example_data('bar')) %>% 
  cjs_tooltip(label = 'label_text',
              title = 'title_text', beforeTitle = 'beforeTitle_text', afterTitle = 'afterTitle_text',
              footer = 'footer_text', beforeFooter = 'beforeFooter_text', afterFooter = 'afterFooter_text')
```


```{r}
chartjs() %>%
  cjs_add_bars(x = letters, y = numbers, label = 'Data 1', data = cjs_example_data('bar')) %>% 
  cjs_add_bars(x = letters, y = numbers, label = 'Data 2', data = cjs_example_data('bar')) %>% 
  cjs_tooltip(label = 'x value: ${x}, y value: ${y}', 
              title = 'Dataset: ${label}', 
              footer = 'take with a grain of salt')
```

## Interaction modes

> How the tooltips are shown

The default, no real need to do this unless you want to be explicit.

```{r}
cjs_example_data('bar', grouped = TRUE) %>% 
  chartjs(type = 'bar', x = letters, y = numbers, group = group) %>% 
  cjs_interaction_mode('point')
```

Highlight the group at a particular index e.g. A, B or C ..

```{r}
cjs_example_data('bar', grouped = TRUE, shuffle = TRUE) %>% 
  chartjs(type = 'bar', x = letters, y = numbers, group = group) %>% 
  cjs_interaction_mode('index') %>% 
  cjs_tooltip(title = 'All data in ${x}')
```

Highlight the dataset group.

```{r}
cjs_example_data('bar', grouped = TRUE, shuffle = TRUE) %>% 
  chartjs(type = 'bar', x = letters, y = numbers, group = group) %>% 
  cjs_interaction_mode('dataset') %>% 
    cjs_tooltip(title = 'All data in: ${label}')
```
